\documentclass{article}

\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{parskip}
\usepackage{varwidth}
\usepackage{ifthen}
\usepackage{amssymb}
\usepackage{color}
\usepackage[Q=yes]{examplep}
%\usepackage{fullpage}


% NOTE:
% -----
%
%     Only project reports of TPM and Camera project are submitted through this page.
%
%     All submissions must be anonymous, both your solutions and your gradings
%     of other solutions.
%
%     Your answer sheet must also include the question. Copy and paste the
%     questions from your personal problems sheet.
%
%     You may replace your uploaded file as many times as you want before the
%     deadline.
%
%     It is not possible to upload documents after the deadline.
%
%     You will be able to see the projects to grade after the solutions deadline.
%
%     You will be able to see your grade result after the result deadline, but
%     you can always see your uploaded gradings.
%
%     Uploaded files must be PDF.
%
% Think about the following when you do the grading:
% --------------------------------------------------
%
%     If you deduct points, motivate this such that the person you grade
%     understands why points are deducted.
%
%     If you give full points, just say e.g., "Yes, this agrees with the
%     information on page XX or slide XX or http://...". Be specific about the
%     source which you have used to verify the answer.
%
%     Some answers can not be immediately found any material but are instead
%     based on understanding a certain concept. In this case, make an effort to
%     verify the correctness by understanding the concept yourself.
%
%     If you are unsure about the grading, say why but be generous when giving
%     points.
%
% Post-grading procedures:
% ------------------------
%
%     You are welcome to discuss the grading of your project with Ben or Jonathan
%     and we are willing to modify your grade if you motivate why (and the
%     motivation is reasonable). In order to facilitate a fruitful discussion
%     this will be done during the office hours written on the webpage.
%
%     Discussing your result with Ben does not have a deadline and can be done at
%     any time during the course (but please respect the office hours).  If your
%     score is modified it will not be seen on this page, but can be seen on the
%     result summary on the course webpage.

\newcommand{\grade}[5]{
  % Heading with identifier of grading criterion and max points.
  \textbf{Grading criterion; #1 (#3p):}\textit{#4}

  % Print reason behind grade.
  #5
  % Print awarded score.
  \hfill
  \begin{varwidth}{\linewidth}
    \textbf{Points: #2/#3}
  \end{varwidth}
}

\newcommand{\QAN}[5]{
  % Question par.
  \textit{Q#1}:#3  \\
  % Answer part.
  \ifthenelse{\equal{#2}{C}}{
    \def \grading {\Large\textcolor{green}{\checkmark}\normalsize}
  }{
    \def \grading {\Large\textcolor{red}{\textbf{x}\hspace{0.142cm}}\normalsize}
  }
  \textit{A:}#4\hfill\grading \\
  % Note part.
  \textit{Note:}#5
}

\newcommand{\escape}[1]{\PVerb{#1}}

\begin{document}
  % Title.
  \begin{center}
    \huge{Review -- Project: TPM} \\
    \vspace{0.2cm}
    \Large{\today}
    \vspace{0.4cm}
    \hrule
  \end{center}
  % End title.

  \grade{assignment 1}{3}{5}
  {
    Report describes the necessary steps to repeat the group's
    experimental setup.
  }
  {
    The description is a bit terse, would probably suffice for anyone already
    comfortable with virtual machines, Linux and the TPM.
  }

  \grade{generating EK}{2}{2}
  {
    Report should contain a dump EK and description how it was obtained.
  }
  {
    Contains both.
  }

  \grade{dump SRK public key}{0}{2}
  {
    Report should contain a dump SRK pubkey and description how it was
    obtained.
  }
  {
    Nothing about the SRK public key in the report.
  }

  \grade{Key hierarchy questions}{6}{6}
  {
    Each correct answer to the questions equals 2 points.
  }
  {
    \QAN{1}{C}{
      Difference between identity and signature keys?
    }
    {
      One of the differences between the two is that the identity key is used
      for attestation while the signature key is used to sign user data.
    }
    {
      ''Signing keys only for signing'' (L4 -- 59), Attestation identity
      key involved in remote attestation (L5 -- 23).
    }

    \QAN{2}{C}{
      Which keys can be used for file encryption?
    }
    {
      Legacy keys and storage keys can be used for file encryption.
    }
    {
      TPM key types (L4 -- 59).
    }

    \QAN{2}{C}{
      There is one type of key that exists, but is not recommended. Which key
      is that, and why does it exist?
    }
    {
      Legacy keys. The legacy keys exist because of the fact that they are
      compatible with older system.
    }
    {
      Combination of ''There was a TPM version 1.0 but we can today forget
      about that version'' (L4 -- 53) and ''Legacy: [...] (compatible with TPM
      v1)'' (L4 -- 59).
    }
  }

  \grade{Key hierarchy -- Possible combinations}{2}{2}
  {}
  {
    \QAN{}{C}{
      Are all combinations possible? if not, why?
    }
    {
      The key named C could not be created. The reason for this is that a non
      migratable key can not be a child of a migratable key.
    }
    {
      Creating non-migratable keys with migratable parent as base should return
      \texttt{TPM\_INVALID\_KEYUSAGE} (TPM-part3 -- p.74).
    }
  }

  \newpage

  \grade{Key hierarchy -- Correct drawing}{2}{2}
  {
    Drawing / representation of correct hierarchy.
  }
  {
    Representation is correct, does not include the C - key.
  }

  \grade{Key migration - questions}{8}{10}
  {
    Each correct answer gives 2 points.
  }
  {
    \QAN{1}{C}{
      Is it possible for a migratable key to be the parent of a non-migratable
      key?
    }
    {
      No, it is not possible for a migratable key to be the parent of
      non-migratable keys. When a key is migrated, all of its children are
      migrated as well. Thus, all children of a migratable key have to be
      migratable
    }
    {
      Creating non-migratable keys with migratable parent as base should return
      \escape{TPM_INVALID_KEYUSAGE} (TPM-part3 -- p.74).
    }

    \QAN{2}{C}{
      Which command is the first to be executed when performing a key
      migration?
    }
    {
      \escape{TPM_CreateMigrationBlob} is the command that implements the first
      step in the process of moving a key to a new parent or platform.
    }
    {
      Correct according to description (TPM-part2 -- p.85).
    }

    \QAN{3}{F}{
      Give a short description of the command \escape{TPM_ConvertMigrationBlob}
    }
    {
      This command takes migration blob and creates a normal wrapped blob. The
      migrate blob must be loaded into the TPM using the normal
      \escape{TPM_loadKey} function.
    }
    {
      One point deduction due to \escape{TPM_loadKey} being deprecated and \\
      \escape{TPM_loadKey2} should be used instead (TPM-part3 -- p.318).
    }

    \QAN{4}{F}{
      Which TPM command load the migrated keys into the TPM?
    }
    {
      \escape{TPM_loadKey}
    }
    {
      Same as above, \escape{TPM_loadKey} is deprecated, should use
      \escape{TPM_loadKey2} instead.
    }

    \QAN{5}{C}{
      Is it the TPM or the TSS that handles the transfer of the migration blob?
    }
    {
      The TSS handles the transfer of the migration blob.
    }
    {
      Since the TPM only handles conversion of input and output data, the
      transfer of the resulting/necessary data is handled by the software stack
      (TSS). A more motivated answer wouldn't hurt.
    }
  }

  \grade{Key migration -- migration \& documentation}{1}{2}
  {
    Do the key migration specified in the project instructions and document it
    (Q1).
  }
  {
    Commands are cut off, seems to be ok but can't be verified.
  }

  \grade{Key migration -- remaining questions}{2}{4}
  {}
  {
    \QAN{2}{F}{
      When do you use a key of type \escape{TPM_KEY_USAGE = TPM_Migrate}?
    }
    {
      When using migration authority.
    }
    {
      While the answer is 'correct' it is a bit short.  \\
      The \escape{TPM_KEY_USAGE = TPM_Migrate} is used to restrict a specific
      key in such a way that it can only be used in the \escape{TMP_MigrateKey}
      function. Since this function performs the function of a migration
      authority with limited knowledge about the key, the physical security of
      the executing system is assumed to be high (TPM-part3 p.93).
    }

    \QAN{3}{F}{
      What is the rewrap option option of the \escape{migrate} command used
      for?
    }
    {
      The rewrap option is use to directly move a key to a new parent.
    }
    {
      Missing explanation on what enables the key to be 'directly moved' to
      another parent. The flag tells the TPM to re-wrap
      (decrypt$\rightarrow$encrypt) the key with a new parent, which enables
      that parent to load the key as a normal encrypted element (TPM-part3
      p.85).
    }
  }

  \grade{Extending values to the PCRs -- Questions}{4}{4}
  {}
  {
    \QAN{1}{C}{ % Question
      Describe one TPM command that can be used to extend the SHA-1 digest to a
      PCR.
    }{ % Answer
      The \escape{TPM_Extend} command can be used to extend the SHA-1 digest to
      a PCR by adding a new measurement to a PCR.
    }{ % Note
      Correct (TPM-part3 p.160).
    }

    \QAN{2}{C}{ % Question
      Describe one TPM command that can be used to read a PCR value.
    }{ % Answer
      The \escape{TPM_PCRread} command can be used to read a PCR value.
    }{ % Note
      Correct (TPM-part3 p.162)
    }
  }

  \grade{Extending the PCRs -- PCR 'overflow'}{1}{2}
  {
    Run \escape{sha -if <filename> -ix <PCR index>} on a large file and show
    the result.
  }{
    The figure shows that the command has been run, but since it is run on \\
    \escape{text.txt} and there is no indication of then file size of the file
    it's hard to figure out if the run illustrated the functionality or not.
  }

  \grade{File encryption -- Questions}{3}{6}
  {}
  {
    \QAN{1}{C}{ % Question
      Why is \escape{TSS_Bind} a TSS command, and not a TPM command?
    }{ % Answer
      The encryption is done outside of the TPM and is therefor not a TPM
      command.
    }{ % Note
      Correct (L5 - p.11).
    }

    \QAN{2}{F}{ % Question
      Give some difference between data binding and data sealing.
    }{ % Answer
      Data binding uses a symmetric key for encryption and data sealing uses
      asymmetric encryption.
    }{ % Note
      Could not verify that this is true, and since sealing is binding but
      where the data is locked to a given PCR state, it should be the same type
      of encryption?
    }

    \QAN{3}{F}{ % Question
      Can a key used for data sealing be migrated to another TPM?
    }{ % Answer
      No, because sealing data to one TPM platform makes it illegal to migrate
      a key to another TPM.
    }{ % Note
      Deducting one point because the answer makes it sound like no migration
      is possible after sealing any data on a TPM. The key used to seal the
      data can not be migrated (L5 -- p.2).
    }
  }

  \grade{TPM -- Data binding}{4}{4}
  {}
  {
    \QAN{1}{C}{ % Question
      Why does the key have to be loaded inside the TPM when decrypting, but
      not when encrypting?
    }{ % Answer
      When encrypting, only the public key is needed, while decryption uses the
      private key, which is not accessible outside of the TPM.
    }{ % Note
      This makes sense, since this is how asymmetric cryptography works.
    }

    \QAN{2}{C}{ % Question
      Migrate the binding key to TPM2 and see if the file can be decrypted
      there.
    }{ % Answer
      To be able to decrypt the binding key is needed. Since the binding key
      was migrated to TPM2, the file was able to be decrypted there too.
    }{ % Note
      Should be possible.
    }
  }

  \grade{TPM -- Data sealing}{4}{4}
  {}
  {
    \QAN{1}{C}{ % Question
      Test if you can do a sealing with a legacy key, a binding key or a
      signing key. If not, why?
    }{ % Answer
      It was not possible to do a sealing with a legacy key, binding key or
      signing-key. The reason for this is that sealing only can be done with
      storage keys.
    }{ % Note
      \begin{quote}
        If the keyUsage field of the key indicated by the keyHandle dose not
        have the value \escape{TPM_KEY_STORAGE} the TPM must return the error
        code \escape{TPM_INVALID_KEYUSAGE}.

        \hfill
        -- Documentation of \escape{TPM_Seal} (TPM-part3 p.63)
      \end{quote}
    }

    \QAN{2}{C}{ % Question
      Now migrate the storage key to TPM2 and see if you can unseal the file
      there too. Explain what you observe.
    }{ % Answer
      The storage key is not migratable and could therefor not be migrated to
      TPM2. Since TPM2 did not have access to the storage key, unsealing was
      not achieved.
    }{ % Note
      \begin{quote}
        If the keyHandle points to a migratable key then the TPM MUST return
        the error code \escape{TPM_INVALID_KEYUSAGE}.

        \hfill
        -- Documentation of \escape{TPM_Seal} (TPM-part3 p.63)
      \end{quote}
    }
  }

  \grade{TPM -- Authentication}{4}{6}
  {}
  {
    \QAN{1}{C}{ % Question
      In the above, could the \escape{verifyfile} command been done by another
      TPM?
    }{ % Answer
      Yes it is possible because only the public key is used.
    }{ % Note
      The usage string for verifyfile agrees with only using public part:
      \escape{verifyfile [-ss info|der] -is <sig file> -if <data file> -ik
      <pubkey file (.pem)>}.
    }

    \newpage

    \QAN{2}{C}{ % Question
      Which TPM command is used to decrypt the file?
    }{ % Answer
      The command that is used to decrypt files is \escape{TPM_UnBind}.
    }{ % Note
      Same decryption command as earlier.
    }

    \QAN{3}{F}{ % Question
      Can the decryption based authentication be done by using data sealing
      instead of binding?
    }{ % Answer
      No it can not because the TPMs have different PCR values.
    }{ % Note
      Sealing can work to identify a TPM. If a user encrypts a piece of data
      with the public part of the key, only the TPM that has the correct
      private part and is in the correct measured configuration state can
      decrypt it and return the data. Which in turn proves that it's the same
      TPM, with the same configuration.
    }
  }

  \grade{Signing}{2}{2}
  {
    Use \escape{signfile} and \escape{verifyfile} to sign and verify a text
    file.
  }
  {
    Presented commands are correct.
  }

  \grade{Encryption}{2}{2}
  {
    Use \escape{bindefile} and \escape{unbindfile} to encrypt and decrypt a
    text file.
  }
  {
    Presented commands are correct.
  }

  \grade{Attestation -- signature}{2}{2}
  {
    Use the \escape{identity} and \escape{quote} commands to create an AIK and
    use that to quote a PCR value.
  }
  {
    Provided commands are correct.
  }

  \grade{Attestation -- encryption}{2}{2}
  {
    Use the \escape{createkey -ix}, \escape{sealfile} and \escape{unsealfile}
    commands to bind a hash-digest for a file to a storage key. Unseal the
    original file, which should work. Modify the file and extend the PCR with
    the new file, the unsealing should fail.
  }
  {
    The correct commands are provided.
  }

  \grade{Creating a TPM program}{2}{4}
  {
    Provide correctly working program with source code and documentation to
    repeat the work.
  }
  {
    Only a small snippet provided, which should work. Should instruct where
    rest of the code is.
  }

  \textbf{Total: 52/67}

\end{document}
