\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage{fullpage}

\begin{document}
	\section{Peer review -- adsec03}
	 \begin{tabular}{| l | c | c |}
        \hline
        \textbf{Description} & \textbf{Max possible} & \textbf{Awarded} \\
        \hline
        \hline
        \input{../input/peer1.tex}
    \end{tabular}

    % Too much text will cap results, too little undefined but bad?
    % 7*0.75=5.25 NOK, consequences unclear
    % 7*1.25=8.75 OK
    % 7*1.40=9.8 NOK, will cap grade to grade 6

    \subsection{Deduction motivations}
      \noindent
      \textit{\textbf{General note:} The amount of whitespace used in this
      report in order to try to stretch it over the requirement (which it
      doesn't?) is really pushing it. Don't really know how this should be
      handled since the grading only says that; under 4.5 pages (lower-bound)
      or under 5.25 pages (higher-bound) is ''not OK'', is that failing the whole
      report or something else?} \\

      \noindent
      Section only lists motivations for deductions to save space.

    	\begin{itemize}
    		\item{\textbf{A}
          Really thin on information, but technically has all
          sections except summary (-1). Not clear how second assumption relates
          to security.
        }
    		\item{\textbf{B}
          Vague environment description (-1). Missing requirements stated in project
          document (-1).}
        \item{\textbf{C} ''out-of-hands-reach'' assumption not referenced in
          security evaluation (-1). Authentication specified without
          assumption/specification (-1).
        }
    		\item{\textbf{D1}
          No life-cykel management (-1). No TPM secret/auth values mentioned
          (-1).
        }
    		\item{\textbf{D2}
          Unclear what ''send the information to the user securely'' entails
          (-1). TOE is a laundry-list of components without descriptions of
          relevant security impact (-2). ST is only a list of statements, no
          descriptions or reasoning (-1).
        }
    		\item{\textbf{E1}
          No descriptions of the evaluation/threats except names in table (-2).
          Summary missing
          (-2). Final result/rational unclear (-1).
        }
    		\item{\textbf{E2}
          Not covering all the stated threats (-2). SECURE BOOT not described
          in architecture (-2).
        }
    	\end{itemize}
\end{document}
